---
title: "Your Mom's House Analysis, Part II"
#author: "Kevin Magnan"
#date: "10/12/2020"
output: html_document
---
Published on October 12th, 2020

I'm back, Jeans! For those who missed [part I](https://www.kevinjmagnan.com/YMH.html) of this two part YMH analysis, I followed along with Eric Ekholm's blog post to pull YouTube speech-to-text captions for a playlist of YMH videos. If you missed the warning, this is NSFW content so tread lightly all you cool cats and kittens. 

Now that we have the caption data, it's time to really dive into the text data and see what we can learn about Tom and Christine. Like last time, I am going to follow along with [Eric's second YMH blog post](https://eric-ekholm.netlify.app/blog/ymh-explore/) where he analyzed this data and find opportunities to learn from him as well as unpack the data in other ways.

Before we get off on this analysis, there are a few important observations of the text data we should mention:
* The episode transcripts are automatically created by Youtube’s speech-to-text model. It’s usually really good, but it does make some mistakes & obviously has trouble with proper nouns (e.g. TikTok).
* The speakers of each phrase are not tagged or timestamped. That is, there are no indications whether it’s Tom, Christina, or someone else speaking any given line.
* I’m only looking at the episodes available on Youtube, and the most recent episode I’m including is episode 572 with Chris Distefano, aka Chrissy Drip Drop, aka Chrissy one-and-done, aka Chrissy vodka soda.

That's enough Cool Guy talk for one day, let's get started with some data cleaning and manipulation.

# Setup and data work

```{r warning = FALSE, message=FALSE}
library(tidyverse)
library(lubridate)
library(tidytext)
library(tidylo)
library(igraph)
library(ggraph)
library(vroom)
library(readr)

##ymh <- vroom("~/blog_data/ymh_data.csv")
## delete before posting 
ymh <- vroom("~/GitHub/kjmagnan1s.github.io/blog_data/ymh_data.csv")

ymh_single_row <- ymh %>% 
  group_by(title, episode) %>%
  summarise(text = str_c(text, collapse = " ") %>%
              str_to_lower()) %>%
  ungroup()
```

# Descriptives

We have a total of 175 observations, or episodes, worth of data to investigate, ranging from episode 345 to 572. Let's take a look at some descriptives about YMH episodes.

```{r warning = FALSE, message = FALSE}
ep_length <- ymh %>%
  group_by(ep_no) %>%
  summarise(minutes = (max(start) + max(duration))/60) %>%
  ungroup()

ep_length %>%
  ggplot(aes(x = ep_no, y = minutes)) +
  geom_point(color = "black") +
  geom_line(color = "black") +
  labs(
    title = "YMH Episode Length",
    x = "Episode Number",
    y = "Length (mins)"
  )

## looks like we have an outlive episode. checking on ep_ling$episodes, I found that there's a break between in subtitles generation between approx. episode 330 and 394. Let's go ahead and remove all episodes below 394 moving forward and try this again

ymh <- ymh %>% filter(ep_no > 393)

ep_length <- ymh %>%
  group_by(ep_no) %>%
  summarise(minutes = (max(start) + max(duration))/60) %>%
  ungroup()

ep_length %>%
  ggplot(aes(x = ep_no, y = minutes)) +
  geom_point(color = "black") +
  geom_line(color = "black") +
  labs(
    title = "YMH Episode Length",
    x = "Episode Number",
    y = "Length (mins)"
  )

## much better
```  
  
From the plot, it's clear that around episode 450 the length of episode began to increase to upwards of 250 minutes (4 hours!) before plateauing at around 150 minutes. It's interesting to see such wide variability in episode length, instead of stepped changes. There are a lot of lows and highs among episode lengths, symptomatic of a person on Meth as Dr Drew would point out. With this much variability, let's fit a smooth line to the plot.

```{r}
ep_length %>%
  ggplot(aes(x = ep_no, y = minutes)) +
  geom_point(color = "black") +
  geom_line(color = "black") +
  geom_smooth(color = "blue") +
  labs(
    title = "YMH Episode Length",
    x = "Episode Number",
    y = "Length (mins)"
  ) 
```
  
It appears that episode length hit it's peak around episode 480, at which point they leveled off at ~150 minutes.

How about the 
  
  
  






