---
title: "Your Mom's House Analysis, Part II"
#author: "Kevin Magnan"
#date: "10/12/2020"
output: html_document
---
Published on October 12th, 2020

I'm back, Jeans! For those who missed [part I](https://www.kevinjmagnan.com/YMH.html) of this two part YMH analysis, I followed along with Eric Ekholm's blog post to pull YouTube speech-to-text captions for a playlist of YMH videos. If you missed the warning, this is NSFW content so tread lightly all you cool cats and kittens. 

Now that we have the caption data, it's time to really dive into the text data and see what we can learn about Tom and Christine. Like last time, I am going to follow along with [Eric's second YMH blog post](https://eric-ekholm.netlify.app/blog/ymh-explore/) where he analyzed this data and find opportunities to learn from him as well as unpack the data in other ways.

Before we get off on this analysis, there are a few important observations of the text data we should mention:
* The episode transcripts are automatically created by Youtube’s speech-to-text model. It’s usually really good, but it does make some mistakes & obviously has trouble with proper nouns (e.g. TikTok).
* The speakers of each phrase are not tagged or timestamped. That is, there are no indications whether it’s Tom, Christina, or someone else speaking any given line.
* I’m only looking at the episodes available on Youtube, and the most recent episode I’m including is episode 572 with Chris Distefano, aka Chrissy Drip Drop, aka Chrissy one-and-done, aka Chrissy vodka soda.

```{rr warning = FALSE, message = FALSE}
library(tidyverse)
library(lubridate)
library(tidytext)
library(tidylo)
library(igraph)
library(ggraph)
library(vroom)

theme_set(theme_classic())

ymh <- vroom("~/blog_data/ymh_data.csv")

## delete before posting ymh <- vroom("C:/Users/kEVIN/Documents/GitHub/kjmagnan1s.github.io/blog_data/ymh_data.csv")

ymh_subset <- ymh %>% 
  group_by(title, episode) %>%
  summarise(text = str_c(text, collapse = " ") %>%
              str_to_lower()) %>%
  ungroup()
```

```{r}
ep_length$episode <- replace(ep_length$episode, 122, "Ep. 520 Melissa Villasenor")
```

```{r warning = FALSE, message = FALSE}
ep_length <- ymh %>%
  group_by(episode) %>%
  summarise(minutes = (max(start) + max(duration))/60) %>%
  ungroup()

ep_length %>%
  ggplot(aes(x = episode, y = minutes)) +
  geom_line(color = 'black')+
  geom_point(color = 'steelblue') +
  labs(
    title = "YMH Episode Length",
    x = "Episode Number",
    y = "Length (mins)"
  )
```  
  
  
  
  
  
  
  
  
  






