---
title: "Migrate Data with R + API"
description: |
  Documenting my journey completing a data migration leveraging R and Salesforce's API.
  
author:
  - name: Kevin Magnan
    url: https://twitter.com/KevinMagnan
date: "08-27-2022"
categories:
  - R
  - Salesforce
  - API
  - ETL
base_url: https://www.kevinjmagnan.com
preview: preview.svg
draft: no
output:
  distill::distill_article:
    self_contained: false
    toc: true
---

```{r global-options, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      warning = FALSE, 
                      message = FALSE,
                      R.options = list(width=80),
                      fig.align="center")
```

Published on August xx, 2022

Very often, I am impressed or shocked to learn a new feature or problem {R} can solve. My most recent realization was {R} is a fantastic data migration tool. {R} is undoubtably a powerful tool when it comes to data cleaning and manipulating. Combine this superpower with the ability to connect to a legacy SQL database and push, via an API, clean ETL data into a new Salesforce environment and you've got the makings of a secure and effective data migration from a single tool.

## Library setup

Before diving in too deep, let's begin with the set-up. My favorite package for loading libraries is {pacman} because it allows me to list all my packages in a single statement. Additionally, {pacman} will install packages you do not currently have installed as well as install any updates from CRAN (or github) before loading into your environment.

```{r load libraries}
## load multiple libraries and check on updates
pacman::p_load(
  # allows connectivity between database and R, required by dplyr
  DBI,
  # simplified sql language
  dplyr,
  # provide DBI backend to any ODBC connection
  odbc,
  # leverage Salesforce API to migrate data
  salesforcer,
  # nifty library to secure credentials
  keyring,
  # may be helpful for connecting to API
  httr,
  httpuv,
  # clean messy data, alternatively install tidyverse
  tidyr
)
```

## Database Setup

Whether or not you happen to have a SQL database sitting at your home or place of work, I found it incredibly easy to interact with and query a SQL database from R and RStudio. This was my first opportunity in either a personal or professional setting to interace with a databse in R and, while there are some frustrating learning curves, I found the entire process extremely efficient and productive. 

As a point of best practices, remember when connecting to databases, APIs, or other credentialized environments to never save your passwords or secret keys in your script. While I was researching the SQL connection via R, I found a cheeky little library called {keyring} which made saving my sensitive credentials super easy. Combining a password manager with {keyring} should be more than sufficient to secure your logins.

Final note when connecting to SQL databases; I found that occassionally the connection would fail or the tables would not populate. Refreshing the connection (via RStudio) or disconnecting and reconnecting once or twice always solved this issue.

```{r connect to SQL database}
# establish credentials
key_set(service = "service_name",
        username = "user_name")

# name the connection something short and easy to reuse later
con <- dbConnect(odbc(),
                 Driver = "SQL Server", 
                 Database = "TSN",
                 Server = "54.85.208.115",
                 UID = key_list("service_name")[1,2],
                 PWD = key_get("service_name", "user_name")
                 )
```

## Salesforce API setup
Leverage the SalesForce API and [Salesforcer](https://stevenmmortimer.github.io/salesforcer/) library in R
```{r connect to Salesforce api}
# authorize the RStudio console to connect with Salesforce API via logging in with basic credentials or OAuth2.0
sf_auth(login_url = "https://[your-domain].my.salesforce.com")

## test access
# save user info
user_info <- sf_user_info()
# print Organization ID from user info 
sprintf("Organization Id: %s", user_info$organizationId)
# print User ID from user info 
sprintf("User Id: %s", user_info$userId)
# print your Token
salesforcer_state()$token

## Useful function to check errors and confirm completed jobs - print API bulk calls from your Salesforce connection
sf_get_all_jobs_bulk()
```







